Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
text

In \cite{DBLP:journals/corr/AbateBCCDKK16}, Abate et al.  focus on
synthesising stabilising controllers for continuous plants
by exploiting advantage in bit-accurate verification of software-implemented 
digital control~\cite{Bessa16}.  While they also make use of a CEGIS-based 
technique, their approach is restricted to synthesising controllers for hybrid 
closed-loop systems that are stable and only consider transfer function models.  
In contrast, in the current paper, we consider a state-space
representation of the physical system, which allows us to synthesise controllers that
make the closed-loop system \emph{safe} as well as stable.  Moreover, 
a key aspect of the second approach we evaluate
is that we integrate abstraction
refinement inside the CEGIS loop.

@@

Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
Feedback architectures can be employed to affect the properties and behaviours of the continuous process (the plant) of interest.   
%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
We are interested in the synthesis of digital feedback, 
as implemented on modern FPGAs or ICs. 
The most basic feedback architecture is the state feedback, 
where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
%
\begin{equation}
\label{eq:controlaction}
u_k = r_{k} - K x_k. 
\end{equation}
%
Here $K \in \mathbb{R}^{m \times n}$ is a feedback gain matrix, 
and $r_{k}$ is a reference signal (again digital).   
%
The closed-loop model then takes the form 
\begin{align}
\label{eq:closedloopss}
x_{k+1} = ( A_d - B_d K ) + B_d r_k.
\end{align}
The gain matrix $K$ can be set so that the closed-loop digitalised dynamics are shaped as desired, 
for instance according to a specific stability goal or around a specific dynamical behaviour \cite{astrom1997computer}. 
As argued later, in this work, we will target more complex objectives, such as quantitative safety requirements that are not typical in the digital control literature.

@@

Asymptotic stability boils down to Lyapunov stability and convergence to an equilibrium point\cite{Astrom08} %\todo{add reference}.  
Lyapunov stability requires that model trajectories remain in a neighbourhood of the equilibrium point. 
In the case of closed-loop LTI models as in \eqref{eq:closedloopss}, 
the equilibrium point is the origin (if the reference is equal to zero), or an offset thereof.  
In this paper, we consider systems with a reference signal equal to zero.

@@

\end{array}\right]$ & , $\left[\begin{array}{c}

>>>>

The work in \cite{DBLP:journals/corr/AbateBCCDKK16} investigates the synthesis of 
stabilising controllers for continuous plants described as transfer functions, 
by exploiting bit-accurate verification of software-implemented 
digital controllers~\cite{Bessa16}.  While this work also make use of a CEGIS-based technique, 
the approach is restricted to synthesising digital controllers for stable 
closed-loop systems described via transfer function models.  
In contrast, in the current paper we consider a state-space representation of the physical system, 
which is known to be more general \cite{Astrom08} and allows to synthesise controllers that
make the closed-loop system \emph{safe}.  Moreover, 
this work  integrates an abstraction/refinement step inside the main CEGIS loop.

@@

Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
Feedback architectures can be employed to affect the properties and behaviours of the continuous process (the plant) of interest.   
%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
We are interested in the synthesis of digital feedback, 
as implemented on modern FPGAs or ICs. 
The most basic feedback architecture is the state feedback, 
where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
%
\begin{equation}
\label{eq:controlaction}
u_k = r_{k} - K x_k. 
\end{equation}
%
Here $K \in \mathbb{R}^{m \times n}$ is a feedback gain matrix, 
and $r_{k}$ is a reference signal (again digital).   
%
The closed-loop model then takes the form 
\begin{align}
\label{eq:closedloopss}
x_{k+1} = ( A_d - B_d K ) x_k + B_d r_k.
\end{align}
The gain matrix $K$ can be set so that the closed-loop digitalised dynamics are shaped as desired, 
for instance according to a specific stability goal or around a specific dynamical behaviour \cite{astrom1997computer}. 
As argued later, in this work, we will target more complex objectives, such as quantitative safety requirements that are not typical in the digital control literature.

@@

Asymptotic stability boils down to Lyapunov stability and convergence to an equilibrium point~\cite{Astrom08}.  %\todo{add reference}.  
Lyapunov stability requires that model trajectories remain in a neighbourhood of the equilibrium point. 
In the case of closed-loop LTI models as in \eqref{eq:closedloopss}, 
the equilibrium point is the origin (if the reference is equal to zero), or an offset thereof.  
In this paper, we consider systems with a reference signal equal to zero.

@@
